
---
title: "main.r"
author: "JohnHadish"
date: "3/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Testing The Program:
Each Function should have its own demonstration script: 

Download Data:
```{r}
myGenotype=read.table(file="http://zzlab.net/GAPIT/data/mdp_numeric.txt",head=T)
myPosition=read.table(file="http://zzlab.net/GAPIT/data/mdp_SNP_information.txt",head=T)
myPhenotype=read.table(file="http://zzlab.net/GAPIT/data/CROP545_Phenotype.txt",head=T)
myCovariate=read.table(file="http://zzlab.net/GAPIT/data/CROP545_Covariates.txt",head=T)
```

```{r}
library(plotly)
library(ggplot2)
library(gridExtra)
library(knitr)
```

Description: 
returns: P: a vector n long of p values for every gene in n
Dependent: Generate_PCA, Scree, Determine_Linear_Dependent
```{r, Run_GLM}
# prcomp is a default principle component analysis
allPC <- prcomp(myGenotype[,-1])
# pcThreshold removes all princople components that account for less than threshold
threshPC <- pcThreshold(allPC)

# pcCovariance  determines if covariates are linear with principle components
finalPC <- pcCoVariance(threshPC, myCovariate, .7)

P <- Run_GLM(myGenotype, myPhenotype[,2], finalPC)


color.vector <- rep(c("deepskyblue","orange","forestgreen","indianred3"),10)
m=nrow(myPosition)
plot(t(-log10(P))~seq(1:m),col=color.vector[myPosition[,2]])
```

```{r, Determine_PC_Number}


```


returns: unknown
```{r, Determine_linear_dependent}

Determine_Linear_Dependent(PC, C)
```



Returns: a QQ plot of observed and expected p values
```{r, Plot_QQ}
Plot_QQ(P)
```

Returnes: Manhatten plot
```{r, Plot_ Manhatten}
Plot_Manhatten(I, P)
```

P_Threshold
returns: how many true positives are above the first false positive
```{r}
```

