
---
title: "main.r"
author: "JohnHadish"
date: "3/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Testing The Program:
Each Function should have its own demonstration script: 

Download Data:
```{r}
myGenotype=read.table(file="http://zzlab.net/GAPIT/data/mdp_numeric.txt",head=T)
myPosition=read.table(file="http://zzlab.net/GAPIT/data/mdp_SNP_information.txt",head=T)
myPhenotype=read.table(file="http://zzlab.net/GAPIT/data/CROP545_Phenotype.txt",head=T)
myCovariate=read.table(file="http://zzlab.net/GAPIT/data/CROP545_Covariates.txt",head=T)
```

Load Dependencies and Packages:
```{r, message = FALSE, warning = FALSE}
library(plotly)
library(ggplot2)
library(gridExtra)
library(knitr)

library(devtools)
install_github("JohnHadish/DJ.GLM.GWAS")
library(DJ.GLM.GWAS)
```

Run GWAS using GLM and Correlation on the provided data:
```{r, Run_GLM}
# prcomp is a default principal component analysis
allPC <- prcomp(myGenotype[,-1])
# pcThreshold removes all princpal components that account for less than threshold
threshPC <- pcThreshold(allPC)
# pcCovariance  determines if covariates are linear with principal components
finalPC <- pcCoVariance(threshPC, myCovariate, .7)
P <- GWASbyGLM(myGenotype, myPhenotype[,2], finalPC)

# GWAS by Correlation
P2 <- GWASbyCor(myGenotype[,-1], myPhenotype[,-1])
```
P and P2 contains the p-values corresponding to the two competing methods GWASbyGLM and GWASbyCor for the association tests between phenotype and markers. Markers are tested one at a time with covariates in C included as covariates.
This package GWASbyGLM also performs PCA and incorporates PCs as cofactors for GWAS.  Also,it automatically excludes the PCs that are in linear dependent to the covariates. 


# Manhattan Plots of GWAS by GLM and Cor
```{r}
plotManhatten(P, main = "GWAS by GLM")
plotManhatten(P2, main = "GWAS by Cor")
```
 

Returns: a QQ plot of observed and expected p values
```{r, Plot_QQ}
par(mfrow=c(1,2))
plotQQ(P, main = "GWAS by GLM")
plotQQ(P2, main = "GWAS by Cor")
```

30 GWAS Simulations
```{r}
# These only need to be calculated 1 time since they only pertain to structure of Genotype
allPC <- prcomp(myGenotype[,-1])
threshPC <- pcThreshold(allPC)
finalPC <- pcCoVariance(threshPC, myCovariate, .7)

#Create BLINK input data
GD=t(myGenotype[,-1])
write.table(GD,file="myData.dat",quote=F,sep="\t",col.name=F,row.name=F)
write.table(myPosition,file="myData.map",quote=F,sep="\t",col.name=T,row.name=F)

scoresTop10 = matrix(NA,3,30)
time30 = matrix(NA,3,30)

total <- 30
# create progress bar
pb <- txtProgressBar(min = 0, max = total, style = 3)
for(i in 1:30)
{
  simP <- G2P(myGenotype[,-1],0.75,alpha=1,NQTN=10,distribution = "norm")


  ### Run Correlation GWAS###
  simCor_Time_Start <- proc.time()
  simCor <- GWASbyCor(myGenotype[,-1], simP$y)
  simCor_Time_End <- proc.time()
  
  ### Run GLM GWAS###
  simGLM_Time_Start <- proc.time()
  simGLM <- GWASbyGLM(myGenotype, simP$y, finalPC )
  simGLM_Time_End <- proc.time()
  
  ### Run BLINK GWAS####
  simBLINK_Time_Start <- proc.time()
    # write this phenotype for BLINK to use:\
  P_BLINK <- data.frame(myPhenotype[,1], simP$y)
  names(P_BLINK)[1] <- "Taxa"
  names(P_BLINK)[2] <- "Obs"
  write.table(P_BLINK, file="myData.txt",quote=F,sep="\t",col.name=T,row.name=F)
  # # Blink rewrites files, so I have to recreate them every time if I wantit to run
  write.table(GD,file="myData.dat",quote=F,sep="\t",col.name=F,row.name=F)
  write.table(myPosition,file="myData.map",quote=F,sep="\t",col.name=T,row.name=F)
  # Run Blink on the command line, read in results
  system("/home/john/Documents/ZZClass/BLINK/blink_linux --gwas --file myData --numeric", wait = TRUE, ignore.stdout = TRUE, ignore.stderr = TRUE)
  GMP <- read.delim("Obs_GWAS_result.txt", head = T)
  simBLINK <- t(as.matrix(GMP[,5]))
  simBLINK_Time_End <- proc.time()
  
  time30[2,i] = simCor_Time_End[3] - simCor_Time_Start[3]
  time30[1,i] = simGLM_Time_End[3] -simGLM_Time_Start[3] 
  time30[3,i] = simBLINK_Time_End[3] - simBLINK_Time_Start[3]
  
  scoresTop10[2,i] = detectTop10(simCor, simP$QTN.position)
  scoresTop10[1,i] = detectTop10(simGLM,simP$QTN.position)
  scoresTop10[3,i] = detectTop10(simBLINK, simP$QTN.position)

  setTxtProgressBar(pb, i)
}
close(pb)

print(paste("Average of GWAS by Cor average: ", mean(scoresTop10[2,]), "SD: ", sd(scoresTop10[2,]), "Time: ", mean(time30[2,])))
print(paste("Average of GWAS by GLM average: ", mean(scoresTop10[1,]), "SD: ", sd(scoresTop10[1,]), "Time: ", mean(time30[1,])))
print(paste("Average of GWAS by BLINK average: ", mean(scoresTop10[3,]), "SD: ", sd(scoresTop10[3,]), "Time: ", mean(time30[3,])))
```

```{r}
system("R CMD Rd2pdf --output=./Reference_Manual.pdf .")
```

