---
title: "main.r"
author: "JohnHadish"
date: "3/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Testing The Program:
Each Function should have its own demonstration script: 

Download Data:
```{r}
myGenotype=read.table(file="http://zzlab.net/GAPIT/data/mdp_numeric.txt",head=T)
myPosition=read.table(file="http://zzlab.net/GAPIT/data/mdp_SNP_information.txt",head=T)
myPhenotype=read.table(file="http://zzlab.net/GAPIT/data/CROP545_Phenotype.txt",head=T)
myCovariate=read.table(file="http://zzlab.net/GAPIT/data/CROP545_Covariates.txt",head=T)
```


Description: 
returns: P: a vector n long of p values for every gene in n
Dependent: Generate_PCA, Scree, Determine_Linear_Dependent
```{r, Run_GLM}
Run_GLM(X, y, C)
```

returns: principle components after skree analysis
```{r, Determine_PC_Number}
Determine_PC_Number(X, )
```


returns: unknown
```{r, Determine_linear_dependent}

Determine_Linear_Dependent(PC, C)
```



Returns: a QQ plot of observed and expected p values
```{r, Plot_QQ}
Plot_QQ(P)
```

Returnes: Manhatten plot
```{r, Plot_ Manhatten}
Plot_Manhatten(I, P)
```

P_Threshold
returns: how many true positives are above the first false positive
```{r}
```





